---
title: "Lead Training"
toc: true
params:
  leadName: "Kenneth Bakari"
  leadEmail: "kennethbakari@phaseoneconsultants.com"
  leadMgrName: "Anita Tate"
  leadMgrEmail: "anita.tate@shelbycountytn.gov"
---

Some amount of lead-based paint (LBP) certification is required for all contractors involved in our home repair programs.

::: {.callout-important appearance="simple"}
- An [EPA/HUD RRP Certificate](docs.qmd#RRP) is required for **all** rehab and lead jobs. 
- [TDEC Firm certification](docs.qmd#TDEC) is required for only lead jobs.
:::

To get an RRP or Firm license, you must first attend a class by a state-certified lead instructor, and then apply for the appropriate certification.

<details><summary>View a list of accredited Tennessee lead trainers.</summary>
<embed src="../docs/state-lead-trainer-list.pdf" width="600" height="830" 
 type="application/pdf">
</details>

Two companies that offer classes in the Memphis area are [Resolution](https://www.resolutionusa.com/training) and [Phase One](https://phaseoneconsultants.com/).

# Upcoming Classes

Below are upcoming LBP classes held in Memphis.

```{r}
library(gt)

lead_classes <- readr::read_csv("contractors/lead-training-dates.csv")

lead_classes |>
  dplyr::filter(start_date >= lubridate::today()) |>
  dplyr::arrange(start_date) |> 
  gt() |>
  cols_label_with(
    fn = function(x) {
      stringr::str_to_title(x) |> stringr::str_replace_all("_", " ")
    }
  ) |>
  fmt_date(
    columns = ends_with("_date"),
    date_style = "yMd"
  ) |> 
  tab_options(
    table.align = "left",
    table.width = "100%"
  )|> 
  sub_missing()
```

For more information on training offered by Resolution, visit [their website](https://www.resolutionusa.com/training). 

For Phase One classes, email `r params$leadName` at [`r params$leadEmail`](`r paste0("mailto:", params$leadEmail)`).

### Class Locations

Pyramid Place, Memphis, TN (Room TBA)

480 MLK Jr Ave, Memphis, TN 38126

1075 Mullins Station, W-2, Room 263, Memphis, TN 38134

### Class Costs

```{r}
costs <- readr::read_csv("contractors/lead-training-costs.csv")

costs |> 
  gt() |>
  tab_spanner(label = "Resolution",
              columns = c(r_initial, r_refresh)) |> 
  tab_spanner(label = "Phase One",
              columns = c(p_initial, p_refresh)) |> 
  cols_label(
    r_initial = "Initial",
    r_refresh = "Refresher",
    p_initial = "Initial",
    p_refresh = "Refresher"
  ) |> 
  fmt_currency(
    columns = c(2:5), 
    decimals = 0
  ) |>
  tab_options(
    table.align = "left",
    table.width = "100%"
  )
```

Phase One has a \$25 registration fee if you pre-register or \$50 the day of class.

### Registration

To register for a Resolution class, email the below form to email [training@resolutionusa.com](`r paste0("mailto:", "training@resolutionusa.com")`) or fax to 615-868-4140.

<details><summary>View Resolution's registration form.</summary>
<embed src="../forms/resolution-registration.pdf" width="600" height="830" 
 type="application/pdf">
</details>

To register for a Phase One class, email the below form to email `r params$leadName` at [`r params$leadEmail`](`r paste0("mailto:", params$leadEmail)`).

<details><summary>View Phase One's registration form.</summary>
<embed src="../forms/phase-one-registration.pdf" width="600" height="830" 
 type="application/pdf">
</details>

# Training Reimbursement

The SCDH has some funding available for partial reimbursement for Section 3 contractors.

<embed src="../docs/lead-reimbursement-info.pdf" width="600" height="830" 
 type="application/pdf">

To be reimbursed for training, contact `r params$leadMgrName` at [`r params$leadMgrEmail`](`r paste0("mailto:", params$leadEmail)`).

# Certification

After completing the LBP training, you must apply for certification.

RRP certification is obtained through the [EPA](https://www.epa.gov/lead/getcertified). See our [required documents](docs.qmd#RRP) page for instructions on how to apply.

TDEC Firm certification is obtained through the [State of Tennessee](https://www.tn.gov/environment/toxic-substances-program/lead-hazard-program/lead-certification.html). See our [required documents](docs.qmd#TDEC) page for more information.
