---
title: "Lead Training"
toc: true
params:
  leadName: "Kenneth Bakari"
  leadEmail: "kennethbakari@phaseoneconsultants.com"
  leadMgrName: "Anita Tate"
  leadMgrEmail: "anita.tate@shelbycountytn.gov"
---

An EPA/HUD RRP Certificate is required for **all** rehab and lead jobs. TDEC Firm certification is required for only lead jobs.

To get an RRP or Firm license, you must first attend a class by a state-certified lead instructor.

<details><summary>View a list of accredited Tennessee lead trainers.</summary>
<embed src="../docs/state-lead-trainer-list.pdf" width="600" height="830" 
 type="application/pdf">
</details>

# Upcoming Classes

```{r}
library(gt)

lead_classes <- readr::read_csv("contractors/lead-training-dates.csv")

lead_classes |>
  gt() |>
  cols_label_with(
    fn = function(x) {
      stringr::str_to_title(x)
    }
  ) |>
  tab_options(
    table.align = "left"
  )
```

To request classes, email `r params$leadName` at [`r params$leadEmail`](`r paste0("mailto:", params$leadEmail)`).

### Class Locations

480 MLK Jr Ave, Memphis, TN 38126

1075 Mullins Station, W-2, Room 263, Memphis, TN 38134

### Class Costs

Registration Fee is \$25 if you pre-register or \$50 the day of class.

```{r}
costs <- readr::read_csv("contractors/lead-training-costs.csv")


costs |> 
  gt() |>
  fmt_currency(
    columns = c(2:3), 
    decimals = 0
  ) |>
  tab_options(
    table.align = "left"
  )
```

### Registration

To pre-register, email the below form to email `r params$leadName` at [`r params$leadEmail`](`r paste0("mailto:", params$leadEmail)`).

<embed src="../forms/phase-one-registration.pdf" width="600" height="830" 
 type="application/pdf">

Download the completed form and email it to email `r params$leadName` at [`r params$leadEmail`](`r paste0("mailto:", params$leadEmail)`).

# Training Reimbursement

The SCDH has some funding available for partial reimbursement for Section 3 contractors.

<embed src="../docs/lead-reimbursement-info.pdf" width="600" height="830" 
 type="application/pdf">

To be reimbursed for training, contact `r params$leadMgrName` at [`r params$leadMgrEmail`](`r paste0("mailto:", params$leadEmail)`).

# Certification

After completing the LBP training, you must apply for certification.

RRP certification is obtained through the EPA.

TDEC Firm certification is obtained through the State of Tennessee.


